Annotated metamodel for MSR course papers

### 2015-08-06 presentations/paper/paper.tex
Fix Marco's English in abstract

\begin{abstract}
  This should be 100-200 words. Use present or past tense, but use it
  consistently. Prefer ``we'' over ``I'' here and throughout the
  paper. The abstract should summarize the methodology and results;
  see the corresponding sections below. Your paper is preferably
  typeset with LaTeX and it should comply with the Springer LNCS
  style. (That style is also available for word users.) 
\end{abstract}

>>>>

\begin{abstract}
  In 2014, Git surpassed Subversion as the top code management tool
  \cite{EComSurv14}. With many authors collaborating comes the need for an
  appropriate and standardized use of elemental actions, like formulating
  commit messages. Although the official Git documentation states very clear
  guidelines \cite{OffGuide} on how this should be done, maby of users are not
  aware of them or simply ignore them.

  This paper presents a tool that analyzes a set of commit messages regarding
  criteria composed of the official guidelines and some common mistakes, and
  shows a prototypical website that encourages improvements in commit message
  style by creating a competitive score-board for a given GitHub repository. We
  also perform a machine-learning-powered analysis of correlations between the
  criteria, which can help improve the selection of criteria in the future.
\end{abstract}
